# About this report

This content has been loaded from the template report `.Rmd` file. Please edit it at your best convenience!


```{r setup, include=FALSE, eval = TRUE, echo = FALSE}
opts_chunk$set(
  echo=input$report_echo,
  error=TRUE
)
```


```{r, echo = FALSE}
evalDEA <- FALSE

if (exists("DEA")) {
  if(!is.null(DEA$res)){
    evalDEA <- TRUE}
  }
```

# Overview on the data

The data provided was used to construct the following objects

## Samples Selected

The following samples were selected in this analysis : 

<button title="Click to show answer" type="button" onclick="if(document.getElementById('BE_Genus_C.txt') .style.display=='none') {document.getElementById('BE_Genus_C.txt') .style.display=''}else{document.getElementById('BE_Genus_C.txt') .style.display='none'}">Show/hide</button>
<div id="BE_Genus_C.txt" style="display:none">
```{r, echo = FALSE}

kableExtra::kable(SamplesInfoR$metadata$PDX_model)

```
</div>



### Samples Infos 

```{r, echo = FALSE}

write.table(SamplesInfoR$metadata,file = "/tmp/SamplesInfo.csv",sep = ",",quote = FALSE)
br()
xfun::embed_files(path = "/tmp/SamplesInfo.csv", text = "Samples Info file")

```

### Tumor subtypes 

```{r, echo = FALSE}

Tsub_interactive <- ggplot(SamplesInfoR$metadata) +
  aes(x = `Tumor_subtype`, fill =`Tumor_subtype`,tooltip = ..count..) +
  geom_bar() +
  labs(x = "Tumor subtype") +
  coord_flip() +
  theme_gdocs()

  plot(Tsub_interactive)

```

## IHC

```{r, echo = FALSE}


  IHCinteractive <- ggplot(SamplesInfoR$metadata) +
    aes(x = `IHC/patient`, fill =`IHC/patient`,tooltip = ..count..) +
    geom_bar() +
    labs(x = "IHC/patient") +
    theme(legend.position = "none") +
    coord_flip() +
    theme_gdocs()

  plot(IHCinteractive)

```
  
### CNV Technologies distribution
  
```{r, echo = FALSE}

    TechnoPlot <- ggplot(CNVInfoR$metadata) +
    aes(x = `Technology`, fill = `dataset KDI`,tooltip = ..count..) +
    geom_bar() +
    labs(x = "Technology") +
    coord_flip() +
    theme_gdocs()

plot(TechnoPlot)
  
```  
  
### Cisplatin response
  
  
```{r, echo = FALSE}


Cisplatin <- ggplot(SamplesInfoR$metadata) +
  aes(x = `Cisplatin_response`, fill = `labelsCisplatin_response`,tooltip = ..count..) +
  geom_bar_interactive() +
  labs(x = "Cisplatin Response") +
  coord_flip() +
  theme_gdocs() +
  theme(legend.title = element_blank())

plot(Cisplatin)

```
 
```{r,echo = FALSE}

reacAC <- reactive({


 AC <- ggplot(SamplesInfoR$metadata) +
    aes(x = `AC_response`, fill = `labelsAC_response`,tooltip = ..count..) +
    geom_bar_interactive() +
    labs(x = "AC response") +
    coord_flip() +
    theme_gdocs() +
    theme(legend.title = element_blank())

  legend_AC <- get_legend(
    AC +
      guides(color = guide_legend(nrow = 1, keywidth = 5)) +
      theme(legend.position = "top", legend.key.size = unit(2, "cm"),
            legend.box.just ="left",
            legend.title = element_blank(),
            legend.direction = "horizontal",
            legend.spacing.x = unit(1.0, 'cm') )

  )
  return(list(AC,legend_AC))
  
})



  girafe(code = {print(reacAC()[1])})
  
  
```
  
## RNASeq

```{r, echo = FALSE}

write.table(Rawdata$table,file = "/tmp/Rawdata.csv",sep = ",",quote = FALSE)
br()
xfun::embed_files(path = "/tmp/Rawdata.csv", text = "Raw counts matrix")
br()
write.table(Rawdata$table,file = "/tmp/Metadata.csv",sep = ",",quote = FALSE)
xfun::embed_files(path = "/tmp/Metadata.csv", text = "Metadata matrix")



```


# Results 

## RNAseq

### Design

The following design was used:

```{r, echo = FALSE,warning=FALSE}
if (!is.null(Model$formula)){
#DT::datatable(Model$contrast,options = list(scrollX=TRUE))
print(Model$formula)

}
```

### Up-regulated Genes


<button title="Click to show answer" type="button" onclick="if(document.getElementById('UPPS') .style.display=='none') {document.getElementById('UPPS') .style.display=''}else{document.getElementById('UPPS') .style.display='none'}">Show/hide</button>
<div id="UPPS" style="display:none">
```{r, echo = FALSE, warning=FALSE, eval = evalDEA }


kableExtra::kable(DEA$up) %>%
kable_styling() #%>%
# kableExtra::column_spec(1:ncol(DEA$up),width = "80em", bold = FALSE, italic = FALSE)

#DT::datatable(DEA$up,options = list(scrollX=TRUE))
```

```{r, echo = FALSE, warning=FALSE, eval = evalDEA }

write.table(DEA$up,file = "/tmp/Upp_regulated",sep = ",",quote = FALSE)
xfun::embed_files(path = "/tmp/Upp_regulated", text = "Upp regulated genes")

```

```{r, echo = FALSE, warning=FALSE, eval= !evalDEA }

print("Please Run Differential expression analysis first")

```
</div>



# About PDXApp

`PDXApp` is a package containing a Shiny application for
analyzing Patient-Derived-Xenograft data in different conditions and experimental factors.

`PDXApp` was developed by the bio-informatic platform of the Curie's Institute (France). 

## Developers

`PDXApp` is currently maintained by Clément BENOIT and Pierre Gestraud at the Bioinformatic Platform (Institut Curie) (https://curie.fr/).
You can contact them by clicking on the buttons below.

<a href="mailto:mailto:pierre.gestraud@curie.fr?subject=[PDXApp_feedback]" class="btn btn-primary">Pierre Gestraud</a>

<a href="mailto:mailto:clement.benoit@curie.fr?subject=[PDXApp_feedback]" class="btn btn-primary">Clement BENOIT</a>


# Citation info

If you use `PDXApp` for your analysis, please cite it as here below:

```{r}
citation("PdxAppPackage")
```

# Session Information

```{r}
sessionInfo()
```

```{r, echo = FALSE}
library(shiny)
footertemplate <- function(){
  tags$div(
    class = "footer",
    style = "text-align:center",
    tags$div(
      class = "foot-inner",
      list(
        hr(),
        "This report was generated with", tags$a(href="http://bioconductor.org/packages/PDXApp/", "PDXApp"), br(),
        "PDXApp is a project developed by Celine Vallot, Nicolas Servant, Pierre Gestraud, Marangoni Elisabetta and Clement Benoit in the Institut Curie : ",
        br(),
        tags$a(href="https://science.curie.fr/recherche/developpement-cancer-genetique-epigenetique/dynamique-de-linformation-genetique/equipe-vallot/","Vallot Team"),
        br(),
        tags$a(href="https://science.curie.fr/recherche/developpement-cancer-genetique-epigenetique/dynamique-de-linformation-genetique/equipe-vallot/","Bioinformatic Platform (Institut Curie)"),br())
      )
    )
}
```

```{r, echo = FALSE}
footertemplate()
```
